A review on Generative Learning in Computer Vision

### 2020-05-07 paper.tex
done with CGAN

\begin{abstract}
Artificial intelligence has made it possible for computers to learn from experiences and perform simple tasks which a human can easily do. Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers. In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection. Computer Vision (CV) has since been used in numerous ways ranging from automated cars to quality check at factories which usually required an expert to manually check the production line.Artificial intelligence has made it possible for computers to learn from experiences and perform simple tasks which a human can easily do. Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers. In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection.
\end{abstract}

@@

\subsection{Generative Adversarial Networks (GANs)}
Goodfellow et al. developed this state-of-the-art class of neural networks with two key components; a generator and a discriminator. The generator is a neural network which takes a random vector input usually a noise and generates a new plausible output out of it in the domain. This vector input is taken from a Gaussian distribution. A Gaussian or normal distribution is a probability distribution around a mean, which signifies the data around the mean is more frequent as compared to data points away from the mean. A Gaussian distribution shows a bell curve when plotted. The vector is referred as a latent space which means significant variables but not explicity visible. Due to the fact that it uses random vector sample every time, the model becomes stochastic, the output will be non-deterministic every time. The generator makes unlimited samples out of it. The discriminator, a classification model, then takes input from the training dataset as well as output from the generator model and attempts to identify source of the input, whether it is from the training dataset or from the generator generated ouput. Both models are meant to compete with each other, the generator has to fool the discriminator into incorrectly classifying its sample as a real sample from the training set and the discriminator has to make itself perfect in correctly classifying input samples. The generator and the discriminator are both trained alongwith. When the discriminator predicts the class of the input sample, it is tweaked to perform better for the next sample, likewise the generator is updated to create samples which will fool the discriminator. Even though GAN is an unsupervised learning technique but this architecture of it is designed as a supervised learning technique. The generator model is then used discarding the discriminator model.

The following figure \ref{fig1} describes the working of a GAN.

@@

\subsubsection{Conditional GAN}
Conditional GAN is an extension of GAN proposed by Mirza et al. in 2014 \cite{b4}. It works on the principal of conditional probability which is defined as the probability of an event given another event mathematically represented as $P(A|B)$ which translates to probability of $A$ given $B$. Conditional GAN is conditioned using extra information which is passed to the generator as well as to the discriminator. This extra information can be any supplementary information like image labels. The discriminator gets the extra information alongwith the input from generator.

The following figure \ref{fig2} describes the working of a conditional GAN.

>>>>

\begin{abstract}

\end{abstract}

@@

\subsection{Generative Adversarial Networks (GANs)}
Goodfellow et al. developed this state-of-the-art class of neural networks with two key components; a generator and a discriminator. The generator is a neural network which takes a random vector input usually a noise and generates a new plausible output out of it in the domain. This vector input is taken from a Gaussian distribution. A Gaussian or normal distribution is a probability distribution around a mean, which signifies the data around the mean is more frequent as compared to data points away from the mean. A Gaussian distribution shows a bell curve when plotted. The vector is referred as a latent space which means significant variables but not explicity visible. Due to the fact that it uses random vector sample every time, the model becomes stochastic, the output will be non-deterministic every time. The generator makes unlimited samples out of it. The discriminator, a classification model, then takes input from the training dataset as well as output from the generator model and attempts to identify source of the input, whether it is from the training dataset or from the generator generated ouput. Both models are meant to compete with each other, the generator has to fool the discriminator into incorrectly classifying its sample as a real sample from the training set and the discriminator has to make itself perfect in correctly classifying input samples. The generator and the discriminator are both trained alongwith. When the discriminator predicts the class of the input sample, it is tweaked to perform better for the next sample, likewise the generator is updated to create samples which will fool the discriminator. Even though GAN is an unsupervised learning technique but this architecture of it is designed as a supervised learning technique. The generator model is then used discarding the discriminator model. The following figure \ref{fig1} describes the working of a GAN.

@@

\subsubsection{Conditional GAN}
Conditional GAN is an extension of GAN proposed by Mirza et al. in 2014 \cite{b4}. It works on the principal of conditional probability which is defined as the probability of an event given another event mathematically represented as $P(A|B)$ which translates to probability of $A$ given $B$. Conditional GAN is conditioned using extra information which is passed to the generator as well as to the discriminator. This extra information can be any supplementary information like image labels. The discriminator gets the extra information alongwith the input from generator. One of the applications of conditional GAN is generating image of a person given its gender. The following figure \ref{fig2} describes the working of a conditional GAN.
